### 2012-11-09 inst/examples/testing-gp-sdp.Rmd
label methods explicitly

``` {r}
require(reshape2)
df <- data.frame(x = X, Ef = Ef, Y = Y, y_p = y_p, ef = ef, y_m = y_m)
df <- melt(df, id = "x")
ggplot(df)+ geom_jitter(aes(x, value, color = variable)) + geom_point(data = obs, aes(x,y))
````

>>>>

``` {r}
require(reshape2)
df <- data.frame(x = X, direct = Ef, Cholesky = Y, kernlab = y_p, sequential = ef, mlegp = y_m)
df <- melt(df, id = "x")
ggplot(df)+ geom_jitter(aes(x, value, color = variable)) + geom_point(data = obs, aes(x,y))
````
